Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML

### 2014-02-24 paper.tex
Moved full stops to right of citations where they occur at the end of sentences.

The purpose of this paper is to start the high-level design -- and perhaps
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX.\cite{garrett2005ajax}
Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

Domains are the distinct subject matters present in any system
representing large, reusable components and are depicted using a
domain model which shows an organisation of UML packages and their
dependencies.\cite{dickerson2009architecture} The use case diagram and domain model
developed provides a baseline model for a future search application system.

@@

Note that complexity of information for programmes alone.\cite{raimond2009bbc}
A programme to a member of the public could actually refer to an
exact episode or indeed the \emph{brand}, i.e. the title of the programme
in general. An example of a brand would be
\emph{Doctor Who},
\footnote{\emph{Doctor Who} is a popular, long-running science-fiction
television programme produced by the BBC and is frequently sought by users
of the BBC iPlayer television catch-up service after an episode has aired.
} which itself contains multiple series, which in turn
contain a collection of episodes. Note that the brand itself has episodes
as immediate children that do not live under a series, e.g. Christmas specials.
It is also the case that certain things do not have brands or series, e.g.
a film is modelled as a one-off episode.

@@

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonstrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illustration for such a message-based integration
system might be derived from the illustrated patterns created
by Hohpe and Woolf.\cite{hohpe2004enterprise}

@@

The application could go further and interact via a single
SearchResult \emph{facade}\cite{fowler2002patterns} whose
instances provide appropriate responses to canonical hooks
such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
via polymorphic \emph{composition} with different target classes
from the fuller domain model. Given that the search indexes
are likely to take in content from any number of future systems,
there is an appeal to taking a schemaless approach\cite{sadalage2012nosql}
and allow the search application's view layer to display
different kinds of results differently via \emph{duck typing}.
\cite{python2013ducktyping}

@@

Even the models that are presented in this paper do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of Sect.~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology.\cite{beck2001agile}

@@

Some of this hints at a drawback of UML modelling being that it encourages
a lot of design decision at an early stage of a project -- a stage at which we arguably
have the least information.\cite{kelly2013conway} However, there are plenty of
efforts in spite of this that promote modelling and UML being used
compatibly within an Agile process. The use of other modelling techniques
in an Agile setting such as
Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
suggested as suitable in an Agile project.
\cite{ambler2002agile} It may have been more suitable to incorporate
a more diverse range of modelling techniques in the design and analysis
presented so as to find the true strengths of each respective approach.

>>>>

The purpose of this paper is to start the high-level design -- and
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX\cite{garrett2005ajax}.
Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience that appears more responsive.

@@

Domains are the distinct subject matters present in any system
representing large, reusable components and are depicted using a
domain model which shows an organisation of UML packages and their
dependencies\cite{dickerson2009architecture}. The use case diagram and domain model
developed provides a baseline model for a future search application system.

@@

Note that complexity of information for programmes alone\cite{raimond2009bbc}.
A programme to a member of the public could actually refer to an
exact episode or indeed the \emph{brand}, i.e. the title of the programme
in general. An example of a brand would be
\emph{Doctor Who},
\footnote{\emph{Doctor Who} is a popular, long-running science-fiction
television programme produced by the BBC and is frequently sought by users
of the BBC iPlayer television catch-up service after an episode has aired.
} which itself contains multiple series, which in turn
contain a collection of episodes. Note that the brand itself has episodes
as immediate children that do not live under a series, e.g. Christmas specials.
It is also the case that certain things do not have brands or series, e.g.
a film is modelled as a one-off episode.

@@

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the search system demonstrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comprehensively shown in
this format. A better illustration for such a message-based integration
system might be derived from the illustrated patterns created
by Hohpe and Woolf\cite{hohpe2004enterprise}.

@@

The application could go further and interact via a single
SearchResult \emph{facade}\cite{fowler2002patterns} whose
instances provide appropriate responses to canonical hooks
such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
via polymorphic \emph{composition} with different target classes
from the fuller domain model. Given that the search indexes
are likely to take in content from any number of future systems,
there is an appeal to taking a schemaless approach\cite{sadalage2012nosql}
and allow the search application's view layer to display
different kinds of results differently via \emph{duck typing}
\cite{python2013ducktyping}.

@@

Even the models that are presented in this paper do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of Sect.~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology\cite{beck2001agile}.

@@

Some of this hints at a drawback of UML modelling being that it encourages
a lot of design decision at an early stage of a project -- a stage at which we arguably
have the least information\cite{kelly2013conway}. However, there are plenty of
efforts in spite of this that promote modelling and UML being used
compatibly within an Agile process. The use of other modelling techniques
in an Agile setting such as
Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
suggested as suitable in an Agile project\cite{ambler2002agile}.
 It may have been more suitable to incorporate
a more diverse range of modelling techniques in the design and analysis
presented so as to find the true strengths of each respective approach.
